Flexibility of interactions depends on habitat suitability

### 2019-09-12 paper/manuscript.Rmd
Some more sentences to discussion
Make random parameters figures two column wide

```{r fig-random-effects, fig.width = width('single'), fig.height = 2.2*2.5, fig.cap = fig_random_effects_legend}
loadd(random_species_draws)

@@

>>>>

```{r fig-random-effects, fig.width = width('double'), fig.height = 2.2*2, fig.cap = fig_random_effects_legend}
loadd(random_species_draws)

@@

The significant relationship between the number of partners a species has in a hypothetical community with no environmental stress and the slope

* Add in the intro that stress includes how traits mediate environment?
